% Name and contact information
\def\name{Edward Ross}
\def\addrone{}
\def\addrtwo{}
\def\phone{0403 995 808}
%Note cmr10 @ symbol looks funny; sits too high.
\def\email{eddington.ross@gmail.com}

%Font choices
\font\bf = cmbx10 at 14pt
\font\it = cmti10 at 14pt
\font\smallit = cmti10 at 10pt
\font\rm = cmr10 at 14pt

\def\nameReference#1{{\it #1}}

\font\titleFont = pplrc at 24pt
\font\headFont = pplbc8z at 18pt
\font\infoFont = pagk8z at 12pt
\font\sectionFont = ptmb8z at 16pt


\parskip=0pt
\parindent=0pt
\hyphenpenalty5000
\brokenpenalty10000

%A type of section heading: e.g Skills, Experience, Education
\def\head#1{\vskip2pt\hfil\headFont #1\hfill\vskip3pt}

%For skills
\def\startSkill{\relax}
\def\skill#1{\rm {\vskip10pt {\sectionFont #1}}\vskip6pt}
\def\endSkill{\relax}

%For education/academics: Bulleted lists
%Diamond sits a bit low so raise it
\def\bullet{\leavevmode\raise .25ex\hbox{$\diamond$}\kern.5em}
\newdimen\bulletSize
\setbox0=\hbox{\bullet}
\bulletSize=\wd0
\advance\bulletSize by 3pt 
\def\startExp#1#2#3{\rm{\sectionFont #1} \hfill {\it #2}\par\nobreak\vskip1pt\nobreak #3\par\nobreak\vskip2.5pt\nobreak\leftskip=0mm\parskip=1pt}
\def\exp#1{\hangindent=\bulletSize\hangafter=1%Make sure the text lines up
\bullet #1 \par}
\def\endExp{\leftskip=0mm\parskip=0mm\vskip10pt}

\def\description#1{{\rm #1}}


% Header on each page with my information
\def\pageHead{\hfil {\titleFont\name} \hfil
\vskip 3pt
\hrule 
\vskip 5pt
% Temporarily hide address
%{\infoFont\addrone} \hfill {\infoFont\markupEmail{\email}}\par
%{\infoFont\addrtwo} \hfill {\infoFont\phone}\par
{\infoFont\phone} \hfill {\infoFont\markupEmail{\email}}\par
\vskip 2pt}


%Format differently for emailing (pdf) and printing (dvi)
%to take advantages of the capabilities of different media
\ifx\pdfoutput\undefined
\def\markupEmail#1{#1}
\pageHead
\else
%Use eplain and url and color packages
%so we can nicely format email address
\input eplain 
\beginpackages
  \usepackage{url}[2005/06/27]
  \usepackage{color}
\endpackages
\enablehyperlinks
\hlopts{bwidth=0}

\def\markupEmail#1{\href{mailto:#1}{\textcolor{blue}{#1}}}

\setbox100=\vbox{\pageHead}
\topskip=\ht100
\footline = {\tenrm\setbox0=\hbox{\ifx\finished\undefined\smallit Continued $\ldots$\else\relax\fi}\hfill%\folio\advancepageno\hskip-\wd0
\hfill\box0}
\output={\shipout\vbox{\vbox to 0pt{\vskip-22.5pt \pageHead} \pagebody \makefootline}}
\fi


%The body of the text
\rm
\vskip3pt
\head{Objective}
\vskip5pt
\description{Use quantitative modelling and analysis to inform better business decisions}
\vskip5pt

%Improve decision making by transforming data into information. 




\vskip5pt
\head{Professional Experience}
\vskip5pt

\startExp{Haese Mathematics}{Aug 2011--April 2013}{Graduate Developer}
\exp{Developed interactive applications in Java as part of a team}
\exp{Designed and implemented quantitative algorithms}
\exp{Produced multimedia demonstrations of mathematical procedures}
\exp{Contributed to testing, maintenance, and documentation}
%\exp{Maintained C++ code for a graphical application}
%\exp{Prepared software packages for deployment}
\endExp

\startExp{Institute for Telecommunications Research}{Feb--July 2011}{Research intern}
\exp{Implemented and analysed stochastic simulations in MATLAB}
\exp{Presented and reported results of analyses to supervisor}
\exp{Developed methods for generating and measuring complex networks}
\endExp

\startExp{Centre for Organic Photonics and Electronics}{Feb--Aug 2010}{Research student}
\exp{Performed computational simulations of bulk materials}
\endExp

\vskip3pt
\head{Education}
\vskip5pt

%\startExp{Independent education}{2013-present}{}
%\exp{Distinction in Coursera Compilers course; implemented a compiler for an Object Oriented language}
%\exp{Completed ungraded Data Structures and Algorithms course}
%\endExp

\startExp{First Class Honours in Pure Mathematics}{2008--2009}{University of Adelaide}
\exp{University Medal for outstanding academic acheivement}
\exp{Wazir Hasan and Amir Hasan Abdi Prize for highest grade in mathematics}
\exp{Wrote a dissertation expositing a modern area of mathematics}
\exp{Studied specialist courses such as Transform Methods and Signal Processing, and Distribution Theory}
\endExp

\startExp{Bachelor of Science (Physics and Theoretical Physics)}{2005--2007}{University of Adelaide}
\exp{High distinction average (average grade 93\%)}
\exp{Fred Jacka Memorial Prize for highest distinction in final year experimental physics}
%\exp{Dean's Certificate of Merit for outstanding achievement in Physics I}
\endExp

\vfill \break 

\head{Key Skills}
\vskip5pt
\startSkill
\skill{Communication}{
  I enjoy communicating technical concepts to people with a variety of backgrounds and thinking styles. At Haese Mathematics I produced multimedia for school students that uses visual and temporal methods to demonstrate mathematical techniques. I additionally helped produce problems and interactive demonstrations to illustrate, test, and practice concepts.

 In a technical environment I strive to document all code, processes and models I produce so that others can understand, use, and improve on my work.
 }
\skill{Visual Basic for Applications and Excel}{
  In my role at Haese Mathematics I used and helped produce automations of repetitive processes using Visual Basic for Applications, increasing production efficiency. I also worked directly with Excel spreadsheets to manage product data, and as part of the software building process.
}
\skill{Analysing and Presenting Data}{
  My tertiary education in Physics and Mathematics is a solid foundation on the concepts of data analysis, quantitative model construction, and uncertainty and bias in data.

  I have used tools such as Matlab, Python, and domain specific applications to produce simulations, analyse data, and present results. At Haese mathematics I contributed to the development, testing and improvement of user interfaces to applications.

  I have undertaken independent study in algorithms and data structures, and understand their vital role in processing big data in a useful timeframe.
}
\skill{Software Development}{
  At Haese Mathematics I worked in a team to produce and maintain dozens of end user applications, and a few internal software libraries. In this role I gained practical experience reinforcing importance of good design decisions, clear documentation, comprehensive unit testing, and source control. 

  I continually improve my software development knowledge by reading books, learning to use different tools, and engaging with other developers. I strive to develop programs that meet their requirements (including factors such as reliability, efficiency, and usability) quickly.
  
  %I am aware of choosing the right tool for the job; Unix tools for many simple tasks, scripting languages for tasks that need to be done quickly, and languages with solid libraries for complex tasks.
}
\endSkill

\def\finished{\relax}
\vfill\eject

\end
